Who will win the US 2024 election?!!

### 2024-03-14 paper/paper.qmd
file path errors fixed

library(rstan)
library(tidyverse)
library(arrow)
library(dplyr)
library(knitr)
library(ggplot2)

poststrat_data <- arrow::read_parquet("data/analysis_data/poststrat_data.parquet")
survey_data <- arrow::read_parquet("data/analysis_data/survey_data.parquet")
us_election_model <- readRDS(file = "models/single_bay.rds")
```

@@

>>>>

library(rstan)
library(tidyverse)
library(arrow)
library(dplyr)
library(knitr)
library(ggplot2)
library(gutenbergr)
library(haven)
library(labelled)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(broom.mixed)
library(here)

poststrat_data <- arrow::read_parquet(file = here("data/analysis_data/poststrat_data.parquet"))
survey_data <- arrow::read_parquet(file = here("data/analysis_data/survey_data.parquet"))
us_election_model <- readRDS(file = here("models/single_bay.rds"))
```

@@

general_proportion_data <- poststrat_data |>
  group_by(state, sex, age, education, income) |>
  summarise(n = n()) |>
  mutate(prop = n / sum(n))
